### 2016-05-10 tikz/barriersize.tex
slides alpha

\begin{tikzpicture}
  \node[node] (b0l0) {};
  \node[node,below=3 of b0l0] (b0l1) {};
  \node[node,right=of b0l0] (b0r0) {};
  \node[node,below=3 of b0r0] (b0r1) {};
  \node[fit=(b0l0) (b0l1) (b0r0) (b0r1),draw=black,label={90:\huge{$H_{1}$}}] (b0) {};
  \draw[dashed, thick] (b0.north) to (b0.south);

  \node[node,right=of b0r0] (b1l0) {};
  \node[node,below=3 of b1l0] (b1l1) {};
  \node[node,right=12 of b1l0] (b1r0) {};
  \node[node,below=3 of b1r0] (b1r1) {};
  \node[fit=(b1l0) (b1l1) (b1r0) (b1r1),draw=black,label={90:\huge{$H_{2}$}}] (b1) {};
  \draw[dashed, thick] (b1.north) to (b1.south);

  \node[below right=0.1 and 1.3 of b1l0]   (i0) {};
  \node[below=1.5 of i0]     (i1) {};
  \node[right=3 of i0] (i2) {};
  \node[below=1.5 of i2]     (i3) {};
  \node[fit=(i0) (i1) (i2) (i3), draw=black, rectangle, label={90:\huge{$B_{r-1}$}}] (Br2) {};

  \node[below right=0.08 and 0.3 of i0] (i4) {\huge{$\ddots$}};
  \node[below =0.1 of i4] (i5) {};
  \node[right =0.3 of i4]     (i6) {};
  \node[below =0.1 of i6] (i7) {};
  \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {};

  \node[minimum size=12mm,circle,right=of b1r0] (b2l0) {};
  \node[minimum size=12mm,circle,below=3 of b2l0] (b2l1) {};
  \node[minimum size=12mm,circle,right=of b2l0] (b2r0) {};
  \node[minimum size=12mm,circle,below=3 of b2r0] (b2r1) {};

  \node[node,right=of b2r0] (b3l0) {};
  \node[node,below=3 of b3l0] (b3l1) {};
  \node[node,right=of b3l0] (b3r0) {};
  \node[node,below=3 of b3r0] (b3r1) {};
  \node[fit=(b3l0) (b3l1) (b3r0) (b3r1),draw=black,label={90:\huge{$H_{{p}\choose{r}}$}}] (b2) {};
  \draw[dashed, thick] (b1.north) to (b1.south);

@@

  \draw[dashed] (b1l0) to (Br2.west);

  \node[fit=(b0) (b1) (b2), draw=black, label={90:\huge{$B$}},inner sep=12mm] (b) {};
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \node[node] (b0l0) {};
  \node[node,below=3 of b0l0] (b0l1) {};
  \node[node,right=of b0l0] (b0r0) {};
  \node[node,below=3 of b0r0] (b0r1) {};
  \node[fit=(b0l0) (b0l1) (b0r0) (b0r1),draw=black,label={90:\Huge{$H_{1}$}}, inner sep=15mm] (b0) {};
  \draw[dashed, thick] (b0.north) to (b0.south);

  \node[node,right=4 of b0r0] (b1l0) {};
  \node[node,below=3 of b1l0] (b1l1) {};
  \node[node,right=12 of b1l0] (b1r0) {};
  \node[node,below=3 of b1r0] (b1r1) {};
  \node[fit=(b1l0) (b1l1) (b1r0) (b1r1),draw=black,label={90:\Huge{$H_{2}$}}, inner sep=15mm] (b1) {};
  \draw[dashed, thick] (b1.north) to (b1.south);

  \node[above right=1 and 1.2 of b1l0]   (i0) {};
  \node[below=1 of i0]     (i1) {};
  \node[right=3 of i0] (i2) {};
  \node[below=1 of i2]     (i3) {};
  \node[fit=(i0) (i1) (i2) (i3), draw=black, rectangle] (Br2) {\Huge{$B_{r-1}$}};

  \node[below right=0.6 and 1.2 of b1l0]   (i4) {};
  \node[below=1 of i4]     (i5) {};
  \node[right=3 of i4] (i6) {};
  \node[below=1 of i6]     (i7) {};
  \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {\Huge{$B_{r-1}$}};

  % \node[below right=0.08 and 0.3 of i0] (i4) {\Huge{$\ddots$}};
  % \node[below =0.1 of i4] (i5) {};
  % \node[right =0.3 of i4]     (i6) {};
  % \node[below =0.1 of i6] (i7) {};
  % \node[fit=(i4) (i5) (i6) (i7), draw=black, rectangle] (Br3) {};

  \node[minimum size=12mm,circle,right=2 of b1r0] (b2l0) {};
  \node[minimum size=12mm,circle,below=3 of b2l0] (b2l1) {};
  \node[minimum size=12mm,circle,right=2 of b2l0] (b2r0) {};
  \node[minimum size=12mm,circle,below=3 of b2r0] (b2r1) {};

  \node[node,right=3 of b2r0] (b3l0) {};
  \node[node,below=3 of b3l0] (b3l1) {};
  \node[node,right=3 of b3l0] (b3r0) {};
  \node[node,below=3 of b3r0] (b3r1) {};
  \node[fit=(b3l0) (b3l1) (b3r0) (b3r1),draw=black,label={90:\Huge{$H_{{p}\choose{r}}$}},inner sep=15mm] (b2) {};
  \draw[dashed, thick] (b1.north) to (b1.south);

@@

  \draw[dashed] (b1l0) to (Br2.west);
  \draw[dashed] (b1l0) to (Br3.west);

  \node[fit=(b0) (b1) (b2), draw=black, label={90:\Huge{$B_{r}$}},inner sep=15mm] (b) {};
\end{tikzpicture}

### 2016-05-10 tikz/portex.tex
slides alpha

\begin{tikzpicture}
  \node[node] (m1) {$v_{1}$};
  \node[node,right=2cm of m1] (m2) {$v_{2}$};

@@

  \draw[edge] (m1) to node[very near start, above] {0} (e1);
  \draw[edge] (m1) to node[near start, left] {2} (e2);

  \draw[edge] (m2) to node[very near start, above] {1} (e3);
  \draw[edge] (m2) to node[near start, right] {2} (e4);

  \draw[edge] (m1) to node[very near start, below] {1} node[very near end, above] {0} (m2);
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \node[node] (m1) {};
  \node[node,right=2cm of m1] (m2) {};

@@

  \draw[edge] (m1) to node[very near start, above] {\textcolor{green}{0}} (e1);
  \draw[edge] (m1) to node[near start, left] {\textcolor{green}{2}} (e2);

  \draw[edge] (m2) to node[very near start, above] {\textcolor{green}{1}} (e3);
  \draw[edge] (m2) to node[near start, right] {\textcolor{green}{2}} (e4);

  \draw[edge] (m1) to node[very near start, below] {\textcolor{green}{1}} node[very near end, above] {\textcolor{green}{0}} (m2);
\end{tikzpicture}

### 2016-05-10 tikz/regsim.tex
slides alpha

\begin{tikzpicture}
  \node[node] (m1) {$v_{1}$};
  \node[node] (m2) [right = 4cm of m1] {$v_{2}$};
  \node[node] (m3) [right = 4cm of m2] {$v_{3}$};

@@

  \node[node] (r11) [below = 6cm of m1] {$(v_{1},0)$};
  \node[node] (r12) [above = 2cm of r11] {$(v_{1},1)$};
  \node[node] (r13) [below = 2cm of r11] {$(v_{1},2)$};

  \node[node] (l11) [below = 6cm of m3] {$(v_{3},0)$};
  \node[node] (l12) [above = 2cm of l11] {$(v_{3},1)$};
  \node[node] (l13) [below = 2cm of l11] {$(v_{3},2)$};

  \node       (anker) [below = 6.5cm of m2] {};
  \node[node] (mid0) [above right = 1cm and 1cm of anker] {$(v_{2},0)$};
  \node[node] (mid1) [below right = 1cm and 1cm of anker] {$(v_{2},1)$};
  \node[node] (mid2) [below = 3cm of anker] {$(v_{2},2)$};
  \node[node] (mid3) [below left = 1cm and 1cm of anker] {$(v_{2},3)$};
  \node[node] (mid4) [above left = 1cm and 1cm of anker] {$(v_{2},4)$};
  \node[node] (mid5) [above = 3cm of anker] {$(v_{2},5)$};

@@

>>>>

\begin{tikzpicture}
  \node[node] (m1) {};
  \node[node] (m2) [right = 4cm of m1] {};
  \node[node] (m3) [right = 4cm of m2] {};

@@

  \begin{scope}[on background layer]
    \node[fit=(m1),fill=green!50] (cl1) {};
    \node[fit=(m2),fill=yellow!50] (cl2) {};
    \node[fit=(m3),fill=red!50] (cl3) {};
  \end{scope}

  \uncover<3->{
    \node[node] (r11) [below = 6cm of m1] {$0$};
    \node[node] (r12) [above = 2cm of r11] {$1$};
    \node[node] (r13) [below = 2cm of r11] {$2$};

    \node[node] (l11) [below = 6cm of m3] {$0$};
    \node[node] (l12) [above = 2cm of l11] {$1$};
    \node[node] (l13) [below = 2cm of l11] {$2$};

    \node       (anker) [below = 6.5cm of m2] {};
    \node[node] (mid0) [above right = 1cm and 1cm of anker] {$0$};
    \node[node] (mid1) [below right = 1cm and 1cm of anker] {$1$};
    \node[node] (mid2) [below = 3cm of anker] {$2$};
    \node[node] (mid3) [below left = 1cm and 1cm of anker] {$3$};
    \node[node] (mid4) [above left = 1cm and 1cm of anker] {$4$};
    \node[node] (mid5) [above = 3cm of anker] {$5$};

@@

    \only<3>{
      \begin{scope}[on background layer]
        \node[fit=(r11) (r12) (r13),fill=green!50] (cl1b) {};
        \node[fit=(mid0) (mid1) (mid2) (mid3) (mid4) (mid5),fill=yellow!50] (cl2b) {};
        \node[fit=(l11) (l12) (l13),fill=red!50] (cl3b) {};
        \draw[draw=green!50] (cl1.south west) to (cl1b.north west);
        \draw[draw=green!50] (cl1.south east) to (cl1b.north east);
        \draw[draw=yellow!50] (cl2.south west) to (cl2b.north west);
        \draw[draw=yellow!50] (cl2.south east) to (cl2b.north east);
        \draw[draw=red!50] (cl3.south west) to (cl3b.north west);
        \draw[draw=red!50] (cl3.south east) to (cl3b.north east);
      \end{scope}
    }
  }
